Model-based variable selection for regression with highly correlated variables.

### 2014-05-06 www/article13.tex
up comment
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@570 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

 &  &HU &0.4104 & 8.2338 & 0 & 0.53 & 0 & -0.53 & 2.27  \\

@@

 &  &HU &0.4182 & 4.1876 & 11.61 & 4.57 & 4.33 & -0.24 & 16.48  \\

@@

30 & 32 & U & 0.4456 & 2.9154 & 25.23 & 1.92 & 6.5 & 4.58 & 28  \\

@@

 &  &HU &0.5205 & 4.909 & 11.42 & 4.59 & 4.45 & -0.14 & 7.55  \\

@@

 &  &HU &0.5833 & 4.3599 & 17.27 & 2.73 & 14.6 & 11.87 & -2.61  \\

@@

 &  &HU & 0.9623 & 20.9817 & 0 & 0.01 & 0 & -0.01 & 0.02  \\

@@

 &  &HU & 1.1223 & 8.8486 & 12.04 & 3.95 & 3.88 & -0.07 & 3.75  \\

@@

 &  &HU & 1.4343 & 7.3741 & 17.49 & 2.51 & 14.26 & 11.75 & -3.76  \\

@@

 &  &HU &MSE (sd) & 262627.57 (732019) & 10381962.64 (90962496.9) & 262627.57 (732019) \\

@@

 &  &HU &MSE (sd) & 510747.53 (2287539.8) & 603.24 (415.6) & 610.32 (424.9) \\

@@

30 & 32 & U & MSE (sd) & 178323.95 (1426610.2) & 180.02 (44.9) & 141.03 (27.8) \\

@@

 &  &HU &MSE (sd) & 612.72 (291.5) & 207.6 (51.3) & 200.32 (42.6) \\

@@

 &  &HU &MSE (sd) & 555.44 (262.5) & 171.9 (31.1) & 121.08 (11.9) \\

@@

 &  &HU &MSE (sd) & 167.71 (20.6) & 167.98 (20.8) & 167.71 (20.6) \\  

@@

 &  &HU &  MSE (sd) & 168.68 (22.4) & 137.03 (20.3) & 133.49 (12.2) \\

@@

 &  &HU & MSE (sd) & 173.25 (22.9) & 127.4 (11.9) & 110.63 (6.9) \\

@@

 &  &HU &MSE (sd) & 1246.35 (350.5) & 1248.84 (341.4) & 1246.35 (350.5) \\

@@

30 &16& U & MSE (sd) & 712.79 (405.2) & 566.32 (226.4) & 554.01 (257.1) \\

@@

30 & 32 & U & MSE (sd) & 216.12 (128.3) & 157.78 (39.4) & 147.04 (28.4) \\

@@

 &  &HU &MSE (sd) & 274.34 (101.7) & 233.8 (78.9) & 225.64 (67.5) \\

@@

 &  &HU &MSE (sd) & 165.6 (73.7) & 135.84 (24.1) & 123.73 (12.8) \\

@@

 &  &HU &  MSE (sd) & 183.33 (31.1) & 183.78 (31.6) & 183.33 (31.1) \\

@@

 &  &HU &  MSE (sd) & 148.83 (18.6) & 142.97 (22.1) & 139.57 (16.1) \\

@@

 &  &HU & MSE (sd) & 124.29 (19.9) & 118.33 (12) & 111.54 (7.2) \\

@@

 &  &HU & MSE (sd) & 1326.54 (388.4) & 1307.96 (356.6) & 1326.54 (388.4) \\

@@

 &  &HU &MSE (sd) & 1 400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\

@@

30 & 32 & U & MSE (sd) & 855.74 (582.6) & 181.08 (51.9) & 146.79 (32.7) \\

@@

 &  &HU &MSE (sd) & 516.36 (226.6) & 239.77 (103.7) & 228.85 (89.3) \\

@@

 &  &HU &MSE (sd) & 328.7 (146.3) & 169.13 (40.2) & 124.01 (15.4) \\

@@

 &  &HU &  MSE (sd) & 175.93 (25.9) & 176.2 (26.3) & 175.93 (25.9) \\

@@

 &  &HU &  MSE (sd) & 173.65 (25.1) & 143.04 (23.2) & 139.51 (17.6) \\

@@

 &  &HU &  MSE (sd) & 161.92 (25.2) & 127.44 (13.3) & 111.46 (7.2) \\

@@

 &  &HU &MSE (sd) & 1 919.43 (861.8) & 1 885.39 (814) & 1 919.43 (861.8) \\

@@

 &  &HU &MSE (sd) & 696.46 (492.9) & 655.94 (325.7) & 660.93 (354) \\

@@

30 & 32 & U & MSE (sd) & 394.93 (356) & 155.18 (36.4) & 147.81 (30.3) \\

@@

 &  &HU &MSE (sd) & 279.82 (151.1) & 252.35 (108.5) & 239.61 (69.5) \\

@@

 &  &HU &MSE (sd) & 199.3 (158.7) & 136.32 (25.2) & 124.19 (13) \\

@@

 &  &HU &   MSE (sd) & 193.26 (34.9) & 194.43 (37.3) & 193.26 (34.9) \\

@@

 &  &HU &  MSE (sd) & 145.46 (20.1) & 143.74 (23.2) & 140.27 (17.5) \\

@@

 &  &HU &  MSE (sd) & 128.44 (18.4) & 118.61 (11.5) & 111.77 (7.2) \\

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&$P(S)$ &indicator &OLS  &    \textsc{CorReg} $\hat S$ + OLS& \textsc{CorReg} $S$ + OLS\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  &HU &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  &HU &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  &HU &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ &  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  &HU &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  &HU & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator &LAR  &    \textsc{CorReg} $\hat S$ + LAR& \textsc{CorReg} $S$ + LAR\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  &HU &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  &HU &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  &HU &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  &HU &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  &HU &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. }\label{YX2linLASSO}
\end{table}

>>>>

 &  & $BIC_+$ &0.4104 & 8.2338 & 0 & 0.53 & 0 & -0.53 & 2.27  \\

@@

 &  & $BIC_+$ &0.4182 & 4.1876 & 11.61 & 4.57 & 4.33 & -0.24 & 16.48  \\

@@

30 & 32 & $BIC$ & 0.4456 & 2.9154 & 25.23 & 1.92 & 6.5 & 4.58 & 28  \\

@@

 &  & $BIC_+$ &0.5205 & 4.909 & 11.42 & 4.59 & 4.45 & -0.14 & 7.55  \\

@@

 &  & $BIC_+$ &0.5833 & 4.3599 & 17.27 & 2.73 & 14.6 & 11.87 & -2.61  \\

@@

 &  & $BIC_+$ & 0.9623 & 20.9817 & 0 & 0.01 & 0 & -0.01 & 0.02  \\

@@

 &  & $BIC_+$ & 1.1223 & 8.8486 & 12.04 & 3.95 & 3.88 & -0.07 & 3.75  \\

@@

 &  & $BIC_+$ & 1.4343 & 7.3741 & 17.49 & 2.51 & 14.26 & 11.75 & -3.76  \\

@@

 &  & $BIC_+$ &MSE (sd) & 262627.57 (732019) & 10381962.64 (90962496.9) & 262627.57 (732019) \\

@@

 &  & $BIC_+$ &MSE (sd) & 510747.53 (2287539.8) & 603.24 (415.6) & 610.32 (424.9) \\

@@

30 & 32 & $BIC$ & MSE (sd) & 178323.95 (1426610.2) & 180.02 (44.9) & 141.03 (27.8) \\

@@

 &  & $BIC_+$ &MSE (sd) & 612.72 (291.5) & 207.6 (51.3) & 200.32 (42.6) \\

@@

 &  & $BIC_+$ &MSE (sd) & 555.44 (262.5) & 171.9 (31.1) & 121.08 (11.9) \\

@@

 &  & $BIC_+$ &MSE (sd) & 167.71 (20.6) & 167.98 (20.8) & 167.71 (20.6) \\  

@@

 &  & $BIC_+$ &  MSE (sd) & 168.68 (22.4) & 137.03 (20.3) & 133.49 (12.2) \\

@@

 &  & $BIC_+$ & MSE (sd) & 173.25 (22.9) & 127.4 (11.9) & 110.63 (6.9) \\

@@

 &  & $BIC_+$ &MSE (sd) & 1246.35 (350.5) & 1248.84 (341.4) & 1246.35 (350.5) \\

@@

30 &16& $BIC$ & MSE (sd) & 712.79 (405.2) & 566.32 (226.4) & 554.01 (257.1) \\

@@

30 & 32 & $BIC$ & MSE (sd) & 216.12 (128.3) & 157.78 (39.4) & 147.04 (28.4) \\

@@

 &  & $BIC_+$ &MSE (sd) & 274.34 (101.7) & 233.8 (78.9) & 225.64 (67.5) \\

@@

 &  & $BIC_+$ &MSE (sd) & 165.6 (73.7) & 135.84 (24.1) & 123.73 (12.8) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 183.33 (31.1) & 183.78 (31.6) & 183.33 (31.1) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 148.83 (18.6) & 142.97 (22.1) & 139.57 (16.1) \\

@@

 &  & $BIC_+$ & MSE (sd) & 124.29 (19.9) & 118.33 (12) & 111.54 (7.2) \\

@@

 &  & $BIC_+$ & MSE (sd) & 1326.54 (388.4) & 1307.96 (356.6) & 1326.54 (388.4) \\

@@

 &  & $BIC_+$ &MSE (sd) & 1 400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\

@@

30 & 32 & $BIC$ & MSE (sd) & 855.74 (582.6) & 181.08 (51.9) & 146.79 (32.7) \\

@@

 &  & $BIC_+$ &MSE (sd) & 516.36 (226.6) & 239.77 (103.7) & 228.85 (89.3) \\

@@

 &  & $BIC_+$ &MSE (sd) & 328.7 (146.3) & 169.13 (40.2) & 124.01 (15.4) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 175.93 (25.9) & 176.2 (26.3) & 175.93 (25.9) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 173.65 (25.1) & 143.04 (23.2) & 139.51 (17.6) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 161.92 (25.2) & 127.44 (13.3) & 111.46 (7.2) \\

@@

 &  & $BIC_+$ &MSE (sd) & 1 919.43 (861.8) & 1 885.39 (814) & 1 919.43 (861.8) \\

@@

 &  & $BIC_+$ &MSE (sd) & 696.46 (492.9) & 655.94 (325.7) & 660.93 (354) \\

@@

30 & 32 & $BIC$ & MSE (sd) & 394.93 (356) & 155.18 (36.4) & 147.81 (30.3) \\

@@

 &  & $BIC_+$ &MSE (sd) & 279.82 (151.1) & 252.35 (108.5) & 239.61 (69.5) \\

@@

 &  & $BIC_+$ &MSE (sd) & 199.3 (158.7) & 136.32 (25.2) & 124.19 (13) \\

@@

 &  & $BIC_+$ &   MSE (sd) & 193.26 (34.9) & 194.43 (37.3) & 193.26 (34.9) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 145.46 (20.1) & 143.74 (23.2) & 140.27 (17.5) \\

@@

 &  & $BIC_+$ &  MSE (sd) & 128.44 (18.4) & 118.61 (11.5) & 111.77 (7.2) \\

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&$P(S)$ &indicator &OLS  &    \textsc{CorReg} $\hat S$ + OLS& \textsc{CorReg} $S$ + OLS\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  & $BIC_+$ &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  & $BIC_+$ &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ &  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  & $BIC_+$ &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  & $BIC_+$ & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator &LAR  &    \textsc{CorReg} $\hat S$ + LAR& \textsc{CorReg} $S$ + LAR\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  & $BIC_+$ &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  & $BIC_+$ &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  & $BIC_+$ &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  & $BIC_+$ &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ &  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  & $BIC_+$ &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_r}$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_r$&  $P(S)$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$ + Elasticnet& \textsc{CorReg} $S$ + Elasticnet\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & $BIC$ &MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  & $BIC_+$ &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & $BIC$ & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & $BIC_+$ & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & $BIC$ &	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  & $BIC_+$ &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & $BIC$ &MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  & $BIC_+$ &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & $BIC$ & MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  & $BIC_+$ &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & $BIC$ & MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  & $BIC_+$ &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_2}$.}\label{YX2linenet}
\end{table}
